Size Convergence of the E$\times$B \\ Staircase Pattern in Flux Tube \\ Simulations of Ion Temperature \\ Gradient-Driven Turbulence

### 2023-06-22 presentation/presentation.tex
#39: Thermal radius in presentation

		\begin{center}
			\begin{itemize}
				\item <2-> Non-linear flux tube version of Gyrokinetic Workshop (GKW) 
				\item <3-> Circular concentric flux surfaces 
				\item <4-> Standard resolution with 6th order (S6) 
				\item <5-> Cyclone Base Case (CBC) parameters $\rlt = 6.0$ 
				\item <6-> Turbulence level is quantified by the turbulent heat conduction coefficient $\chi$ (normalized by $\rhoth^2 \vth/R$ ($\vth = \sqrt{2 T/m}$)) 
				\item <7-> Quantities $\rhoth$, $R$, $T$, $\vth$ and $m$ are referenced quantities
				\item <8-> Standard box size $(L_\xcoord,~L_\ycoord) = (76.3,~89.8)\,\rhoth$
			\end{itemize}
			\onslide<4->{
			\bigskip
			\begin{tabular}{l | ccccc | ccccc | c | cc}
				& $N_\mathrm{m}$ & $N_x$ & $N_\mathrm{s}$ & $N_{\nu_\parallel}$ & $N_\mu$ & $D$ & $\nu_\mathrm{d}$           & $D_{\nu_\parallel}$ & $D_x$ & $D_y$ & Order & $k_y\rho$ & $k_x\rho$ \\
				\hline
				S6   & 21    & 83    & 16    & 64                  & 9       & 1   & $|\nu_\parallel|$ & 0.2                 & 0.1   & 0.1   & 6     & 1.4       & 2.1       \\
			\end{tabular}}
		\end{center}
	\end{frame}

>>>>

		\begin{center}
			\begin{itemize}
				\item <2-> Non-linear flux tube version of Gyrokinetic Workshop (GKW) 
				\item <3-> Circular concentric flux surfaces 
				\item <4-> Standard resolution with 6th order (S6) 
				\item <5-> Cyclone Base Case (CBC) parameters $\rlt = 6.0$ 
				\item <6-> Turbulence level is quantified by the turbulent heat conduction coefficient $\chi$ (normalized by $\rhoth^2 \vth/R$ ($\vth = \sqrt{2 T/m}$ and $\rhoth = \frac{m \vth}{|q|B}$)) 
				\item <7-> Quantities $\rhoth$, $R$, $T$, $\vth$ and $m$ are referenced quantities
				\item <8-> Standard box size $(L_\xcoord,~L_\ycoord) = (76.3,~89.8)\,\rhoth$
			\end{itemize}
			\onslide<4->{
			\bigskip
			\begin{tabular}{l | ccccc | ccccc | c | cc}
				& $N_\mathrm{m}$ & $N_x$ & $N_\mathrm{s}$ & $N_{\nu_\parallel}$ & $N_\mu$ & $D$ & $\nu_\mathrm{d}$           & $D_{\nu_\parallel}$ & $D_x$ & $D_y$ & Order & $k_y\rho$ & $k_x\rho$ \\
				\hline
				S6   & 21    & 83    & 16    & 64                  & 9       & 1   & $|\nu_\parallel|$ & 0.2                 & 0.1   & 0.1   & 6     & 1.4       & 2.1       \\
			\end{tabular}}
		\end{center}
	\end{frame}
